\begin{frame}[fragile]{Closures}
  \begin{onlyenv}<1>
    \begin{minted}[fontsize = \footnotesize, gobble = 4, frame = lines, framesep
      = 7pt, linenos, breaklines, label = By reference (\texttt{\&T})]{rust}
    let color = "green";
    // A closure to print `color` which immediately borrows (`&`)
    // `color` and stores the borrow and closure in the `print`
    // variable. It will remain borrowed until `print` goes out of
    // scope. `println!` only requires `by reference` so it doesn't
    // impose anything more restrictive.
    let print = || println!("`color`: {}", color);

    // Call the closure using the borrow.
    print();
    print();
    \end{minted}
  \end{onlyenv}

  \begin{onlyenv}<2>
    \begin{minted}[fontsize = \footnotesize, gobble = 4, frame = lines, framesep
      = 7pt, linenos, breaklines, label = By mutable reference (\texttt{\&mut
        T})]{rust}
    let mut count = 0;
    // A closure to increment `count` could take either `&mut count`
    // or `count` but `&mut count` is less restrictive so it takes
    // that. Immediately borrows `count`.
    let mut inc = || {
        count += 1;
        println!("`count`: {}", count);
    };
    // Call the closure.
    inc();
    inc();
    //let _reborrow = &mut count;
    \end{minted}
  \end{onlyenv}

  \begin{onlyenv}<3>
    \begin{minted}[fontsize = \footnotesize, gobble = 4, frame = lines, framesep
      = 7pt, linenos, breaklines, label = By value (\texttt{T})]{rust}
    // A non-copy type.
    let movable = Box::new(3);
    // `mem::drop` requires `T` so this must take by value. A copy type
    // would copy into the closure leaving the original untouched.
    // A non-copy must move and so `movable` immediately moves into
    // the closure.
    let consume = || {
        println!("`movable`: {:?}", movable);
        std::mem::drop(movable);
    };
    // `consume` consumes the variable so this can only be called once.
    consume();
    //consume();
    \end{minted}
  \end{onlyenv}

  \begin{onlyenv}<4>
    \begin{itemize}
    \item \texttt{Fn}: the closure captures by reference (\texttt{\&T})
    \item \texttt{FnMut}: the closure captures by mutable reference
      (\texttt{\&mut T})
    \item \texttt{FnOnce}: the closure captures by value (\texttt{T})
    \end{itemize}
  \end{onlyenv}
\end{frame}
